\section{Scientific Requirements}
\subsection{Geomorphology Measurements}
Of the Mekong River, Mekong Basin, Tonle Sap Lake: Channel bed height \(m\), surface height \(m\), lake surface area \(m^2\), surface flow velocity \(ms^{-1}\). Use of rapidly shot still imagery and Synthetic Aperture Radar.
Of floodplain: Elevation \(m\) , cross sectional profile, surface roughness \(m/100m\). Use to quantify channel migration, bank erosion, and sediment deposition.

\subsection{Solid and Organic Suspensions Measurements}
Organic sediment concentration and grit size distribution \(m^{-2}\)(\% of \(400-800nm\)) wavelength reflected back). Wavelength corresponds to UV-visible which is absorbed greatly by organic grit, and can penetrate water to a certain depth.

\subsection{Biomass estimations}
Of floodplain, normalized Difference Vegetation Index \(m^{-2}\)(\% of \(630-680 nm\), \(780-900nm\)) wavelength reflected back. Vegetation health reflects on time averaged water availability.
mates from ground sampling.
Of water, surface Temperature, Fish shoaling and migration \(m^{-2}\)(\% of \(750-1000nm\)) wavelength reflected back.

\subsection{Data Collection and Analysis Requirements}

    \textbf{Temporal Resolution} Daily to weekly revisit times for all instruments.
    \textbf{Calibration and Validation} Correct interference from the atmosphere. Ensure accuracy and reliability of satellite data with on-the-ground measurements, cross-validation with existing satellite data (MODIS, IKONOS). 
    \textbf{Data Integration} Combine satellite data with historical records and on-the-ground observations, AI-based models for prediction and analysis.